---
title: "PostcodesioR"
output: rmarkdown::github_document
---

[![Travis-CI Build Status](https://travis-ci.org/erzk/PostcodesioR.svg?branch=master)](https://travis-ci.org/erzk/PostcodesioR)
[![Coverage Status](https://img.shields.io/codecov/c/github/erzk/PostcodesioR/master.svg)](https://codecov.io/github/erzk/PostcodesioR?branch=master)
[![Package-License](http://img.shields.io/badge/license-GPL--3-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/PostcodesioR)](https://cran.r-project.org/package=PostcodesioR)

An API wrapper around [postcodes.io](https://postcodes.io/) - free UK postcode lookup and geocoder. This package helps to find and transform information about UK administrative geography like postcodes, LSOA, MSOA, constituencies, counties, wards, districts, CCG or NUTS.

The package is based exclusively on open data provided by postcodes.io. PostcodesioR can be used by data scientists or social scientists working with geocoded UK data. A common task when working with such data is aggregating geocoded data on different administrative levels, e.g. turning postcode-level data into counties. This package can help is achieving this and in many other cases.

## Installation

This package is a developmental version and is available only on GitHub. Hopefully, it will eventually make it to CRAN.
In order to install PostcodesioR use the following commands:

```{r, eval=FALSE}
if(!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("erzk/PostcodesioR")
```

## Loading

To start using the package use the standard command after you installed it.

```{r, warning = FALSE, message = FALSE}
library(PostcodesioR)
```

## Examples

Where possible, I tried to return a data frame. Unfortunately, a lot of API calls return more complex data and in those cases it is safer to use lists. The API uses defaults to limit the number of returned calls. Check the function documentation for more details.

For additional information about the returned data and the function calls see the original [documentation](https://postcodes.io/docs).

The main function of this package provides information related to a given postcode

```{r, message = FALSE, warning = FALSE}
lookup_result <- postcode_lookup("EC1Y8LX")

#overview
str(lookup_result)
```

Check the vignette to see all functions in action.

## Notes

Currently, there is a limit to the number of API calls that can be made. However, [postcodes.io](https://postcodes.io/) provides full list of geolocation data that can be used locally without limitations. The original data is sourced from [Office for National Statistics Data Portal](https://geoportal.statistics.gov.uk/geoportal/catalog/main/home.page).
That [file](https://github.com/ideal-postcodes/postcodes.io/blob/master/latest) is rather large so I didn't include it in the package.

Go to the package's [website](https://erzk.github.io/PostcodesioR/) or to my [blog](https://walczak.org/tag/postcodesior/) for more examples.
