---
title: "README"
author: Eryk Walczak
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/erzk/PostcodesioR.svg?branch=master)](https://travis-ci.org/erzk/PostcodesioR)
[![Coverage Status](https://img.shields.io/codecov/c/github/erzk/PostcodesioR/master.svg)](https://codecov.io/github/erzk/PostcodesioR?branch=master)

# PostcodesioR

This package is a wrapper around [postcodes.io](http://postcodes.io/) which is a free Postcode lookup API and geocoder for the UK.

## Installation

This package is still in a development version and is available only on GitHub. Not sure if it will ever make it to CRAN.
In order to install it use the  following commands:

```{r, eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("erzk/PostcodesioR")
```

## Loading

To start using the package use the standard command after you installed it.

```{r, eval=FALSE}
library(PostcodesioR)
```

## Examples

### Lookup postcodes and outcodes

#### Single postcode

Provide a postcode to obtain all available information: 

```{r, message = FALSE, warning = FALSE}
# load the package
library(PostcodesioR)

lookup_result <- postcode_lookup("EC1Y8LX")

#overview
str(lookup_result)
```

#### Multiple postcodes

```{r}
pc_list <- list(postcodes = c("PR3 0SG", "M45 6GN", "EX165BL"))
bulk_lookup_result <- bulk_postcode_lookup(pc_list)

#overview
str(bulk_lookup_result$result[1])
```

#### Outward code lookup

Provide an outcode to obtain geolocation data for the centroid of the specifid outcode:

```{r}
ocl <- outward_code_lookup("E1")

#overview
str(ocl)
```

### Reverse geocoding

Provide latitude and longitude to obtain geographic information. Different levels of aggregation are available, i.e. postcode or outcode.

#### Single postcode

```{r}
rev_geo <- reverse_geocoding(0.127, 51.507)

# overview
str(rev_geo$result[1])
```

#### Multiple postcodes

```{r, eval = FALSE}
# create a JSON object with the coordinates
geolocations_list <- structure(
 list(
 geolocations = structure(
 list(
 longitude = c(-3.15807731271522, -1.12935802905177),
 latitude = c(51.4799900627036, 50.7186356978817),
 limit = c(NA, 100L),
 radius = c(NA, 500L)),
 .Names = c("longitude", "latitude", "limit", "radius"),
 class = "data.frame",
 row.names = 1:2)),
 .Names = "geolocations")

bulk_rev_geo <- bulk_reverse_geocoding(geolocations_list)

#overview
str(bulk_rev_geo$result)
```

#### Single outcode

```{r}
out_rev_geocode <- outcode_reverse_geocoding("-3.15", "51.47")
# overview
str(out_rev_geocode$result[1])
```

### Generate random entries

#### Postcodes

Generates a data frame with a random UK postcode and corresponding geographic information:

```{r}
# without restrictions
random_postcode()
```

A randomly generated postcode can also belong to a particular outcode:

```{r}
# restrict to an outcode
random_postcode("N1")
```


#### Places

You can also generate a random place, specified by an OSGB code, with corresponding geographic information:

```{r}
random_place()
```


### Postcode validation

This function can validate a UK postcode:

```{r}
postcode_validation("EC1Y 8LX") # actual UK postcode
```


```{r}
postcode_validation("XYZ") # incorrect UK postcode
```


### Find nearest postcodes or outcodes

Provide a postcode to get a list of the nearest postcodes:

```{r}
near_pc <- nearest_postcode("EC1Y 8LX")

#overview
str(near_pc$result[1])
```

You can also use outcodes:

```{r}
near_outcode <- nearest_outcode("EC1Y")
# overview
str(near_outcode$result[2])
```

### Find places

Provide a name of a place of interest. You can specify the number of results (default is 10):

```{r}
place_query_result <- place_query("Hills", limit = 11)

# overview
str(place_query_result$result[1])
```

You can also find a place using an OSGB code:

```{r}
place_lookup_result <- place_lookup("osgb4000000074544700")

# overview
str(place_lookup_result$result)
```

## Notes

Currently there is a limit to the number of API calls. However, postcoes.io provide full list of geolocation data that can be used locally without limitations. Original data is sourced from [Office for National Statistics Data Portal](https://geoportal.statistics.gov.uk/geoportal/catalog/main/home.page).
That [file](https://github.com/ideal-postcodes/postcodes.io/blob/master/latest) is rather large so I didn't include it with the package.

For more info see the original [documentation](https://postcodes.io/docs).
The reference manual can be accessed [here](https://github.com/erzk/PostcodesioR/blob/master/PostcodesioR.pdf).
For more examples of usage go to my [blog](https://walczak.org/tag/postcodesior/).
