---
title: "Introduction"
author: "Eryk Walczak"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    smart: no
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

PostcodesioR is an API wrapper for postcodes.io. It allows acquiring geographic information about the UK postcodes and geographic coordinates.

## Installation

```{r, message = FALSE, warning = FALSE, eval = FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("erzk/PostcodesioR")
```


## Lookup postcodes and outcodes

### Single postcode

Provide a postcode to obtain all available information 

```{r, message = FALSE, warning = FALSE}
library(PostcodesioR)

lookup_result <- postcode_lookup("EC1Y8LX")

#overview
str(lookup_result)
```

There is another function that returns the same data points but returns a list and allows optional parameters

```{r}
query_result <- postcode_query("EC1Y8LX")

#overview
str(query_result)
```

This function creates a nested list with the codes for administrative district, county, ward, parish, parliamentary constituency, CCG, and NUTS.

### Multiple postcodes

To query two or more postcodes, use `bulk_` functions.

```{r}
pc_list <- list(postcodes = c("PR3 0SG", "M45 6GN", "EX165BL"))
bulk_lookup_result <- bulk_postcode_lookup(pc_list)

#overview
str(bulk_lookup_result[1])
```

If you want to work with data frame then the nested list created above can be turned into a data frame

```{r}
library(purrr)

bulk_list <- lapply(bulk_lookup_result, "[[", 2)

bulk_df <-
  map_dfr(bulk_list,
          `[`,
          c("postcode", "longitude", "latitude"))
```

Querying Scottish postcodes requires a separate function:

```{r}
scottish_lookup <- scottish_postcode_lookup("EH12NG")

str(scottish_lookup)
```


### Outward code lookup

Provide an outcode to obtain geolocation data for the centroid of the specified outcode:

```{r}
ocl <- outward_code_lookup("E1")

#overview
str(ocl)
```

## Reverse geocoding

Provide latitude and longitude to obtain geographic information. Different levels of aggregation are available, i.e. postcode or outcode.

### Single postcode

```{r}
rev_geo <- reverse_geocoding(0.127, 51.507)

# overview
str(rev_geo[1])
```

### Multiple postcodes

To reverse geocode multiple values use the function underneath. The result is a nested list, which might be a bit intimidating, but it allows storing unequal number of elements.

```{r}
# create a list with the coordinates
geolocations_list <- structure(
 list(
 geolocations = structure(
 list(
 longitude = c(-3.15807731271522, -1.12935802905177),
 latitude = c(51.4799900627036, 50.7186356978817),
 limit = c(NA, 100L),
 radius = c(NA, 500L)),
 .Names = c("longitude", "latitude", "limit", "radius"),
 class = "data.frame",
 row.names = 1:2)),
 .Names = "geolocations")

bulk_rev_geo <- bulk_reverse_geocoding(geolocations_list)

bulk_rev_geo[[1]]$result[[1]]
```

The list above is not the most common way of storing files. It's more likely that a data frame will be used to store the geodata. In that case, it has to be turned into a list of a specific format required by the API:

```{r}
geolocations_df <- structure(
  list(
    longitude = c(-3.15807731271522, -1.12935802905177),
    latitude = c(51.4799900627036, 50.7186356978817),
    limit = c(NA, 100L),
    radius = c(NA, 500L)),
  .Names = c("longitude", "latitude", "limit", "radius"),
  row.names = 1:2,
  class = "data.frame")

geolocations_df

# turn a data frame into a list
geolocations_df2list <- list(geolocations_df)

# add a list name
names(geolocations_df2list) <- "geolocations"

# display correct input for the function
geolocations_df2list
```


Common usage of this function might be extracting particular variables. You can extract one variable like this:

```{r}
# extract one postcode
bulk_rev_geo[[1]]$result[[8]]$postcode
```

But more likely you will want more than one result. After all, that's the point of using a bulk function:

```{r}
# function to extract variables of interest
extract_bulk_geo_variable <- function(x) {
  bulk_results <- lapply(bulk_rev_geo, `[[`, "result")
  sapply(unlist(bulk_results, recursive = FALSE), `[[`, x)
}

# define the variables you need
variables_of_interest <- c("postcode", "latitude", "longitude")

# return a data frame with the variables
data.frame(
  sapply(variables_of_interest, extract_bulk_geo_variable))
```


### Single outcode

```{r}
out_rev_geocode <- outcode_reverse_geocoding("-3.15", "51.47")
# overview
str(out_rev_geocode[1])
```

## Generate random entries

### Postcodes

Generates a list with a random UK postcode and corresponding geographic information:

```{r}
# without restrictions
random_postcode()
```

A randomly generated postcode can also belong to a particular outcode:

```{r}
# restrict to an outcode
random_postcode("N1")
```

## Places

You can also generate a random place, specified by an OSGB code, with corresponding geographic information:

```{r}
random_place()
```


## Postcode validation

This function can validate a UK postcode:

```{r}
postcode_validation("EC1Y 8LX") # actual UK postcode
```


```{r}
postcode_validation("XYZ") # incorrect UK postcode
```


## Autocomplete postcodes

Find the potential candidates for a postcode if you only know the beginning characters

```{r}
postcode_autocomplete("EC1")
```

It defaults to 10 candidates, but can be changed by specifying the `limit` argument. 

## Find nearest postcodes or outcodes

Provide a postcode to get a list of the nearest postcodes:

```{r}
near_pc <- nearest_postcode("EC1Y 8LX")

#overview
str(near_pc[1])
```

You can also use outcodes:

```{r}
near_outcode <- nearest_outcode("EC1Y")

# overview
str(near_outcode[2])
```

Or longitude and latitude

```{r}
near_ll <- nearest_outcode_lonlat(0.127, 51.507)

#overview
str(near_ll[1])
```


## Find places

Provide a name of a place of interest. You can specify the number of results (default is 10):

```{r}
place_query_result <- place_query("Hills", limit = 11)

# overview
str(place_query_result[1])
```

You can also find a place using an OSGB code:

```{r}
place_lookup_result <- place_lookup("osgb4000000074544700")

# overview
str(place_lookup_result)
```

## Terminated postcodes

You might end up having terminated postcodes in your data set. These are postcodes that are no longer active. UK postcodes can change so it's worth checking whether used postcodes are still active. If you need more information about when a particular postcode was terminated use:

```{r}
terminated_postcode("E1W 1UU")
```
