---
title: "PostcodesioR Introduction"
author: "Eryk Walczak"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## About the package

This package is a wrapper around [postcodes.io](http://postcodes.io/) which is a free Postcode lookup API and geocoder for the UK.

## Install the package

This package is currently uploaded only to GitHub. To install it use the following commands:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("erzk/PostcodesioR")
```

## Usage examples

###

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
